BVP Paper

### 2017-11-27 tex/bvp_paper.tex
writes out ROUGH draft of introduction to BVP paper

\section{Introduction}
\label{sec:intro}
Here we introduce why the timescale problem is hard, and how the choice of initial conditions
vastly effects the amount of time it takes for a solution to get to a meaningful solution

@@

%\bibliography{../biblio.bib}
\end{document}

>>>>

\section{Introduction}
\label{sec:intro}
In many simple studies of convection, the choice of boundary conditions greatly influences the dynamics
of the evolved state.  In studies of incompressible, Boussinesq, \RB convection (RBC), many studies
employ fixed temperature (Dirichlet) boundary conditions at the top and bottom, or fixed heat flux
(Neumann) boundary conditions at both plates.  The former case represents plates of infinite conductivity,
whereas the latter plates of finite conductivity.  In both cases, the choice of symmetric boundary
conditions maintains overall system symettry, and both have been shown to transport heat in nearly the
same manner \cite{johnston&doering2009}.

Studies of convection in stratified systems which aim to model convection in natural, astrophysical systems,
such as that in the outer envelope of low-to-moderate mass stars like the Sun, often employ a mixture of these
two types of boundary conditions (references, references).  The flux at the lower boundary is fixed, modeling
the constant energy generation of the stellar core, while the outer boundary condition is held at a fixed temperature,
effectively allowing all heat generated to escape.

While this setup is a useful model for understanding natural
systems, simulations which employ this setup often suffer from a long convective transient as the thermodynamic structure
of the atmosphere relaxes to the adiabatic profile specified by the fixed temperature upper boundary condition.
This long evolution occurs on the ``Kelvin-Helmholtz,'' or thermal diffusion timescale of the atmosphere, 
$t_{\text{KH}} \approx L_z^2 / \chi$, where $L_z$ is the domain depth and $\chi$ is the thermal diffusivity.
Interesting convection happens as high values of the Rayleigh number, which scales like $\chi^{-1/2}$, such that
in the astrophysically interesting regime of high-Ra, highly stratified convection, evolving a simulation for a
KH time becomes numerically intractable.  As the Rayleigh number increases, the KH time increases while the average
timestep required to resolve the more turbulent flows decreases.  The net result is that under standard initial conditions
of hydrostatic- and thermal- equilibrium, the desired convective solution cannot be obtained and the dynamics of convection
there cannot be studied.

Here we present a method for using simple boundary value problems, along with information about the evolved flow fields,
to fast-forward the slow thermal evolution of convecting simulations.  We present this method in the context of RBC, and
then demonstrate that it applies to stratified, compressible convection under a simple modification.  These methods allow
us to study the convective flows driven by the evolved thermal profile while only requiring initial value problems to run
for long enough to resolve the fast dynamical timescales of convection.

@@

\bibliography{biblio.bib}
\end{document}
